\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-09-26 paper/main.tex
CH: Editing the title page of the paper

\title{\bf  \sffamily \LARGE Evolution of cooperation among individuals with
limited payoff memory\\}
\date{}
\author{Nikoleta E. Glynatsi, Christian Hilbe, Alex McAvoy}

@@

\begin{abstract}
Repeated games are vastly used in evolutionary game theory to explain cooperation
in a variety of environments. Although existing models have shaped our
understanding of human cooperation they often work with idealized assumptions.
In an evolutionary process, individuals imitate other individuals of the
population based on their fitness. It is commonly assumed that an individual
computes their fitness after interacting with a representative sample of the
population and remembering all the interactions they participated in. In real
life we do not always remember all our interactions, instead we rather recall
our most recent ones.

Here we introduce a framework that allows individuals to estimate their fitness
based on a minimum of social information. We explore the difference between our
framework and the classical framework using the iterated prisoner's dilemma. We
show that individuals relying on a single set of information tend to adopt less
generous strategies and they achieve less cooperation than in the classical
scenario. Although strategies in the latter scenario become more cooperative
with increasing benefits, those in the former remain unchanged. We further
explore scenarios where individuals are granted slightly more information, and
our observations indicate that these individuals can attain higher levels of
cooperation.

\end{abstract}

>>>>

\title{\bf  \sffamily \LARGE Evolution of reciprocity among individuals\\ with
limited payoff memory\\}
\date{}
\author{\parbox[c]{16cm}{\centering \onehalfspacing 
Nikoleta E. Glynatsi$^1$, Christian Hilbe$^1$, Alex McAvoy$^{2,3}$\\
$^{\rm 1}$Max Planck Research Group on the Dynamics of Social Behavior,\\ Max Planck Institute for Evolutionary Biology, Pl\"{o}n, Germany \\
$^{\rm 2}$School of Data Science and Society, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599 \\
$^{\rm 3}$Department of Mathematics, University of North Carolina at Chapel Hill,\\ Chapel Hill, NC 27599}}

@@

\begin{abstract}
\noindent
Models of direct reciprocity explain how cooperation can emerge in repeated social dilemmas. 
According to this literature, individuals should naturally learn to adopt conditionally cooperative strategies if further encounters are sufficiently likely.  
While such models have shaped our understanding of cooperation, they often make idealized assumptions on how individuals remember and process information. 
For example, when strategies are transmitted through social learning, it is commonly assumed that individuals update their strategies based on the resulting average payoff.  
This would require them to compute (or remember) their payoffs against all other population members. 
Instead, individuals may sometimes update their strategies based on their most recent experiences only. 
Herein, we introduce a theoretical framework to study the evolution of reciprocity when individuals only learn based on the outcome of their very last interaction. 
%We compare this model to the classical framework based on expected payoffs.  
We show that cooperation can still evolve, but individuals adopt less generous strategies, and they tend to cooperate less often than in the classical framework based on expected payoffs. 
Interestingly, however, we also show that once individuals remember the payoffs of two or three interactions, evolving cooperation rates approach the results of the classical model. 
These findings contribute to a literature that explores which kind of cognitive capabilities are required for reciprocal cooperation. While our results suggest that more memory facilitates the evolution of reciprocity, it only takes a modest amount of payoff memory for cooperation to emerge. 
\end{abstract}

~\\
{\it Keywords:} Evolution of cooperation; direct reciprocity; repeated prisoner's dilemma; social learning; evolutionary dynamics

\clearpage
\newpage
